%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt,a4paper]{awesome-cv}

\geometry{left=1.60cm,top=1.10cm,right=1.60cm,bottom=1.25cm,footskip=14pt}
\colorlet{awesome}{awesome-skyblue}
\definecolor{darktext}{HTML}{252A31}
\definecolor{text}{HTML}{343A40}
\definecolor{graytext}{HTML}{5B6470}
\definecolor{lighttext}{HTML}{7B8490}
\definecolor{sectiondivider}{HTML}{CBD2D9}
\setbool{acvSectionColorHighlight}{true}

% Match the short CV's typography, spacing, and visual hierarchy.
\renewcommand*{\headerfirstnamestyle}[1]{{\fontsize{31pt}{1em}\headerfontlight\color{graytext} #1}}
\renewcommand*{\headerlastnamestyle}[1]{{\fontsize{31pt}{1em}\headerfont\bfseries\color{darktext} #1}}
\renewcommand*{\headerpositionstyle}[1]{{\fontsize{9.5pt}{1em}\bodyfont\scshape\color{awesome} #1}}
\renewcommand*{\headersocialstyle}[1]{{\fontsize{9pt}{1em}\headerfont\color{text} #1}}
\renewcommand*{\sectionstyleface}[1]{{\fontsize{15.5pt}{1em}\bodyfont\bfseries #1}}
\renewcommand*{\entrytitlestyle}[1]{{\fontsize{10.5pt}{1em}\bodyfont\bfseries\color{darktext} #1}}
\renewcommand*{\entrypositionstyle}[1]{{\fontsize{9pt}{1em}\bodyfont\scshape\color{graytext} #1}}
\renewcommand*{\entrydatestyle}[1]{{\fontsize{8.9pt}{1em}\bodyfontlight\slshape\color{graytext} #1}}
\renewcommand*{\entrylocationstyle}[1]{{\fontsize{9.5pt}{1em}\bodyfontlight\slshape\color{awesome} #1}}
\renewcommand*{\descriptionstyle}[1]{{\fontsize{9.6pt}{11.3pt}\bodyfontlight\upshape\color{text} #1}}
\renewcommand*{\skilltypestyle}[1]{{\fontsize{9.6pt}{1em}\bodyfont\bfseries\color{darktext} #1}}
\renewcommand*{\skillsetstyle}[1]{{\fontsize{9.5pt}{1em}\bodyfontlight\color{text} #1}}
\renewcommand{\acvHeaderAfterNameSkip}{1.2mm}
\renewcommand{\acvHeaderAfterPositionSkip}{0.2mm}
\renewcommand{\acvHeaderAfterSocialSkip}{2.5mm}
\renewcommand{\acvSectionTopSkip}{3.5mm}
\renewcommand{\acvSectionContentTopSkip}{2.2mm}
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\renewenvironment{cvitems}{%
  \vspace{-3.2mm}
  \begin{itemize}[leftmargin=2ex,nosep,noitemsep]
    \setlength{\parskip}{0pt}
    \renewcommand{\labelitemi}{\bullet}
    \RaggedRight
}{%
  \end{itemize}
  \vspace{2mm}
}

\hypersetup{
  pdftitle={Emanuele Fabbiani - Long Curriculum Vitae},
  pdfauthor={Emanuele Fabbiani},
  pdfsubject={Curriculum Vitae},
  colorlinks=false
}

\name{Emanuele}{Fabbiani}
\position{Engineer{\enskip\cdotp\enskip}Researcher{\enskip\cdotp\enskip}Founder}
\email{emanuele.fabbiani@gmail.com}
\linkedin{emanuelefabbiani}
\github{donlelef}

\begin{document}

\makecvfooter{Emanuele Fabbiani}{Long Curriculum Vitae}{\thepage}
\makecvheader[C]

\cvsection{Professional Profile}

\begin{cvparagraph}
AI engineer, researcher, and founder who bootstrapped xtream to \textbf{25 employees}, \textbf{EUR 2M+ in annual revenue}, and \textbf{EUR 500K in profit}; built a \textbf{9-person AI team}; and directed \textbf{15+ enterprise AI projects}. Published \textbf{9 peer-reviewed papers with 175+ citations} and delivered \textbf{50+ talks}, combining production ML with company building, enterprise delivery, research, and teaching.
\end{cvparagraph}

\cvsection{Skills}

\begin{cvskills}
  \cvskill{AI/ML}{Machine learning, deep learning, time-series forecasting, GenAI, RAG, ML system design}
  \cvskill{Technologies}{Python, PyTorch, scikit-learn, XGBoost, pandas, Polars, Prefect, Streamlit, GCP, Azure, Databricks}
  \cvskill{Leadership}{Entrepreneurship, AI strategy, enterprise delivery, team building, project management, teaching}
\end{cvskills}

\cvsection{Experience}

\begin{cventries}
  \cventry
    {Co-founder, CEO, and Head of AI}
    {xtream}
    {Milan, Italy}
    {2018--Present}
    {
      \begin{cvitems}
        \item {Co-founded and bootstrapped the company to \textbf{25 employees}, \textbf{EUR 2M+ in annual revenue}, and \textbf{EUR 500K in profit}.}
        \item {Appointed CEO in 2023, doubled revenue in two years, and led the company through its 2025 acquisition by TeamSystem.}
        \item {Built and led a \textbf{9-person AI team} across Italy and Argentina, recruiting three PhDs and two university professors.}
        \item {Launched the GenAI Adoption practice, generating \textbf{EUR 250K in revenue within 15 months} at a \textbf{75\% profit margin}.}
        \item {Directed 15+ enterprise AI projects from presales and team formation through deployment, executive communication, and operational adoption.}
      \end{cvitems}
    }

  \cventry
    {Machine learning, time-series forecasting, Python, XGBoost, SHAP, Azure, Databricks}
    {Financial index forecasting}
    {}
    {}
    {Led five data scientists in designing XGBoost models to forecast financial indexes from macroeconomic variables, using SHAP for model interpretability. Implemented ingestion, preprocessing, training, and prediction on Azure Databricks; selected models outperformed the market and supported investment decisions.\vspace{1.5mm}}

  \cventry
    {Machine learning, time-series forecasting, Python, scikit-learn, project management}
    {Power load forecasting}
    {}
    {}
    {Led four data scientists and data engineers from presales to deployment for Plenitude. Delivered an average MAPE \textbf{25\% lower} than the previous production system, contributing to \textbf{EUR 3M+ lower imbalance penalties}.\vspace{1.5mm}}

  \cventry
    {GenAI, RAG, LangChain, OpenAI, Python, Qdrant}
    {AskHR}
    {}
    {}
    {Led four engineers from presales through deployment of a RAG assistant for Nexi's HR policies. The solution was adopted by all Italian employees and reduced HR ticket volume by \textbf{30\% within two months}.\vspace{1.5mm}}

  \cventry
    {Machine learning, time-series forecasting, XGBoost, SHAP, Prefect, Streamlit, GCP Cloud Run}
    {Sales forecasting}
    {}
    {}
    {Led a \textbf{4-person team} on the Lavazza sales-forecasting project, building XGBoost models with SHAP interpretability that outperformed the prior tools in \textbf{5 out of 5 countries}. Delivered the training pipeline in Prefect and a Streamlit interaction layer deployed on GCP Cloud Run.\vspace{1.5mm}}

  \cventry
    {Credit risk, XGBoost, model validation, production delivery}
    {Credit rating model}
    {}
    {}
    {Led four data scientists and two analysts and subject-matter experts, reporting directly to the CEO of CF+ Bank, to build an XGBoost credit rating model. In backtesting, it delivered \textbf{35\% lower non-performing exposure} than the existing model, \textbf{equivalent to EUR 5M}, and reached production \textbf{two months ahead of schedule}.\vspace{1.5mm}}
\end{cventries}

\newpage
\vspace*{4mm}

\begin{cventries}
  \cventry
    {Co-founder and CEO}
    {Reaidy}
    {Milan, Italy}
    {2024--2025}
    {
      \begin{cvitems}
        \item {Co-founded a GenAI content platform and led product validation, prototyping, initial demos, and enterprise delivery.}
        \item {Secured the first clients and generated \textbf{EUR 150K in first-year revenue} before the company's 2025 acquisition by TeamSystem.}
      \end{cvitems}
    }

  \cventry
    {Data Scientist}
    {Avvale}
    {Milan, Italy and Madrid, Spain}
    {2015--2017}
    {
      \begin{cvitems}
        \item {Delivered data science projects part-time while completing an MSc; expanded the Eni account team from 2 to 8 as contract revenue grew \textbf{5x}.}
      \end{cvitems}
    }

  \cventry
    {Data Scientist}
    {Statwolf}
    {Dublin, Ireland and Pavia, Italy}
    {2015--2017}
    {
      \begin{cvitems}
        \item {Started as a summer intern in Dublin and continued as a part-time remote contributor. Analyzed the effect of weather on semiconductor manufacturing; the findings earned client recognition and follow-up contracts.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Teaching and Academic Service}

\begin{cventries}
  \cventry
    {Professor of Practical AI, MSc in Management \& Innovation}
    {Catholic University of Milan}
    {Milan, Italy}
    {2025--Present}
    {
      \begin{cvitems}
        \item {Teaches the Practical AI course; received \textbf{7.4/9 student satisfaction} in the first year and \textbf{8.4/9} in the second year.}
      \end{cvitems}
    }

  \cventry
    {Academic board member, Economics and Statistics master's programs}
    {Catholic University of Milan}
    {Milan, Italy}
    {2024--Present}
    {
      \begin{cvitems}
        \item {Serves on the academic board for the Economics and Statistics master's programs.}
      \end{cvitems}
    }

  \cventry
    {Lecturer and course designer}
    {University of Pavia}
    {Pavia, Italy}
    {}
    {
      \begin{cvitems}
        \item {Proposed, designed, and taught three editions of Python for Data Science and two of Python for Data Analytics; all five sold out and received \textbf{100\% positive or very positive feedback}.}
        \item {Taught Machine Learning in the MSc in Statistical Genomics.}
      \end{cvitems}
    }

  \cventry
    {Guest lecturer}
    {European universities and colleges}
    {}
    {}
    {
      \begin{cvitems}
        \item {Lectured at the Polytechnic University of Milan, Polytechnic University of Wroclaw, EPFL, HSLU, and Almo Collegio Borromeo.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Education}

\begin{cventries}
  \cventry
    {PhD in Applied Machine Learning}
    {University of Pavia and EPFL}
    {Italy and Switzerland}
    {2018--2021}
    {
      \begin{cvitems}
        \item {Built natural gas forecasting models adopted by A2A and introduced a Bayesian power-grid identification method later extended by ETH and UC Berkeley researchers.}
        \item {Published \textbf{9 peer-reviewed papers with 175+ citations} while building xtream.}
      \end{cvitems}
    }

  \cventry
    {MSc in Embedded and Control Systems}
    {University of Pavia}
    {Pavia, Italy}
    {2015--2017}
    {
      \begin{cvitems}
        \item {Graduated \textbf{110/110 cum laude}; ranked in the faculty's \textbf{top 1\%}.}
      \end{cvitems}
    }

  \cventry
    {BSc in Computer Engineering}
    {University of Pavia}
    {Pavia, Italy}
    {2012--2015}
    {
      \begin{cvitems}
        \item {Graduated \textbf{110/110 cum laude}; ranked in the faculty's \textbf{top 1\%}.}
      \end{cvitems}
    }
\end{cventries}

\newpage
\vspace*{4mm}

\cvsection{Entrepreneurship and Investing}

\begin{cventries}
  \cventry
    {Partner and CTO}
    {PFA}
    {Italy}
    {2026--Present}
    {
      \begin{cvitems}
        \item {Technology leader at a company providing wellbeing and psychological services to businesses and public organizations.}
      \end{cvitems}
    }

  \cventry
    {Angel investor}
    {Pillar}
    {Italy}
    {2025--2026}
    {
      \begin{cvitems}
        \item {Achieved a \textbf{3.3x return in nine months}.}
      \end{cvitems}
    }

  \cventry
    {Pre-seed investor}
    {GoMutuo}
    {Italy}
    {2026--Present}
    {}

  \cventry
    {Advisor}
    {\href{https://www.asimov.law/}{\color{awesome}\faLink\enskip\color{darktext}\underline{Asimov AI}}}
    {Italy}
    {2025--Present}
    {
      \begin{cvitems}
        \item {Advises an AI-native platform for analyzing and monitoring Italian legislation, including complex legislative measures and amendment packages.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Public Speaking and Service}

\begin{cventries}
  \cventry
    {Speaker and track organizer}
    {European AI and Python community}
    {}
    {2022--Present}
    {
      \begin{cvitems}
        \item {Delivered \textbf{50+ talks} at PyData Paris, Berlin, and Milan; PyCon Italy and Germany; AMLD Lausanne; ODSC London; WeAreDevelopers Berlin; Codemotion; Swiss Python Summit; and other European conferences.}
        \item {Organized and hosted conference tracks and workshops at AMLD Lausanne since 2022.}
      \end{cvitems}
    }

  \cventry
    {Mentor}
    {Lead the Future}
    {}
    {}
    {
      \begin{cvitems}
        \item {Selected to mentor bachelor's and master's students interested in STEM careers.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Selected Podcasts}

\begin{cventries}
  \cventry
    {Co-host}
    {\href{https://www.youtube.com/playlist?list=PLJrWo7UCQBWgnQYVWEH8t6-g3fhmvRmF5}{\color{awesome}\faLink\enskip\textbf{AI Compass}}}
    {}
    {}
    {
      \begin{cvitems}
        \item {Hosted a podcast on applied AI and the people building it during his time at xtream.}
      \end{cvitems}
    }

  \cventry
    {Guest}
    {Technology and entrepreneurship podcasts}
    {}
    {}
    {
      \begin{cvitems}
        \item {\href{https://youtu.be/3Sq3XUn8LIw}{\color{awesome}\faLink\enskip\textbf{A Journey Through Academia and Business}} - Data Driven People.}
        \item {\href{https://youtu.be/Q8sw_xTJOH0}{\color{awesome}\faLink\enskip\textbf{How to Build a Company Without External Funding}} - Silicon Valley Fellowship.}
        \item {\href{https://www.youtube.com/live/EVsOkX6SyBk}{\color{awesome}\faLink\enskip\textbf{Using AI to Forecast the Future}} - ProfessionAI.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Selected Talks}

\begin{cventries}
  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems}
        \item {\href{https://youtu.be/FZwOrGD3agA}{\color{awesome}\faLink\enskip\textbf{ML for Energy: Why Academic Models Fail in the Real World}} - AMLD Lausanne.}
        \item {\href{https://youtu.be/k2LDWMLZQ8k}{\color{awesome}\faLink\enskip\textbf{Marketing Media Mix Models with Python \& PyMC: A Case Study}} - PyCon DE \& PyData Berlin.}
        \item {\href{https://youtu.be/NjczVYbtfbg}{\color{awesome}\faLink\enskip\textbf{Advanced Polars: Lazy Loading and Streaming Mode}} - PyData Paris.}
        \item {\href{https://youtu.be/NHdvv3-loV4}{\color{awesome}\faLink\enskip\textbf{System Design for the GenAI Era}} - AI Heroes.}
        \item {\href{https://youtu.be/EPfMHVltAxI}{\color{awesome}\faLink\enskip\textbf{Langfuse, OpenLIT, and Phoenix: Observability for the GenAI Era}} - PyCon Italy.}
        \item {\href{https://youtu.be/hnZjw77-1rE}{\color{awesome}\faLink\enskip\textbf{From SHAP to EBM: Explain Your Gradient Boosting Models in Python}} - Swiss Python Summit.}
        \item {\href{https://youtu.be/r7a4P5ZZRsI}{\color{awesome}\faLink\enskip\textbf{Inside the Mind of an LLM}} - Codemotion.}
        \item {\href{https://youtu.be/k0fzfhRJ2UM}{\color{awesome}\faLink\enskip\textbf{The Hitchhiker's Guide to Asyncio}} - PyCon Italy.}
      \end{cvitems}
    }
\end{cventries}

\cvsection{Public Resources}

\begin{tcolorbox}[
  colback=awesome!4!white,
  colframe=sectiondivider,
  boxrule=0.4pt,
  arc=1.5mm,
  left=2mm,
  right=2mm,
  top=1.6mm,
  bottom=1.6mm
]
  \centering
  {\fontsize{9.2pt}{1em}\bodyfont
    \href{https://scholar.google.com/citations?user=aK8MDJIAAAAJ}{\color{awesome}\faGraduationCap\enskip\color{darktext}\underline{Research}}
    \quad\textcolor{sectiondivider}{\textbar}\quad
    \href{https://github.com/donlelef}{\color{awesome}\faGithub\enskip\color{darktext}\underline{Code}}
    \quad\textcolor{sectiondivider}{\textbar}\quad
    \href{https://sessionize.com/emanuele-fabbiani/}{\color{awesome}\faMicrophone\enskip\color{darktext}\underline{Speaking}}
    \quad\textcolor{sectiondivider}{\textbar}\quad
    \href{https://youtube.com/playlist?list=PLbrceUOJLNLSlZfIWXZCdXzTeVw3JSurG}{\color{awesome}\faYoutube\enskip\color{darktext}\underline{Talks}}
    \quad\textcolor{sectiondivider}{\textbar}\quad
    \href{https://medium.com/@donlelef}{\color{awesome}\faPenNib\enskip\color{darktext}\underline{Articles}}
  }
\end{tcolorbox}

\end{document}
