%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
\documentclass[10pt,a4paper]{awesome-cv}

\geometry{left=1.25cm, top=0.9cm, right=1.25cm, bottom=1.2cm, footskip=.4cm}

\definecolor{tiel}{HTML}{1AEAC8}
\definecolor{softtiel}{HTML}{E8FFFB}
\definecolor{cvdarktext}{HTML}{222222}
\definecolor{cvtext}{HTML}{333333}
\definecolor{cvgraytext}{HTML}{555555}
\definecolor{cvlighttext}{HTML}{666666}
\colorlet{awesome}{tiel}
\colorlet{sectiondivider}{tiel}
\colorlet{darktext}{cvdarktext}
\colorlet{text}{cvtext}
\colorlet{graytext}{cvgraytext}
\colorlet{lighttext}{cvlighttext}

\setbool{acvSectionColorHighlight}{true}
\renewcommand{\acvHeaderSocialSep}{\quad{\color{tiel}\textbar}\quad}
\renewcommand{\acvHeaderAfterSocialSkip}{4mm}
\renewcommand{\acvSectionTopSkip}{2.6mm}
\renewcommand{\acvSectionContentTopSkip}{2mm}

\newcommand{\metric}[1]{\colorbox{softtiel}{\strut\textbf{#1}}}
\newcommand{\resource}[2]{\textbf{#1}: \url{#2}}

\name{Emanuele}{Fabbiani}
\position{Researcher{\enskip\cdotp\enskip}Entrepreneur{\enskip\cdotp\enskip}Engineer}
\email{emanuele.fabbiani@gmail.com}
\extrainfo{\href{https://www.linkedin.com/in/emanuelefabbiani}{https://www.linkedin.com/in/emanuelefabbiani}}

\begin{document}
\makecvheader[C]

\cvsection{Skills}
\begin{cvskills}
  \cvskill{Core skills}{Data science, machine learning and deep learning for tabular data, time series forecasting, software engineering, and AI engineering.}
  \cvskill{Technical skills}{5+ years: Python, Python data science ecosystem (pandas, polars, scikit-learn, XGBoost, PyTorch), Google Cloud Platform, ML system design and development. 2+ years: GenAI system architecture and development.}
  \cvskill{Soft skills}{Entrepreneurship, public speaking, project management up to EUR 3M, group management in academia and business, and teaching.}
\end{cvskills}

\cvsection{Experience}
\begin{cventries}
  \cventry
    {xtream}
    {Co-founder, CEO, and Head of AI}
    {Milan, Italy}
    {2018--current}
    {xtream was a consulting company building digital products and AI solutions for scaleups and corporates. Bootstrapped the company with four partners and grew it to over \metric{EUR 2M} in annual revenue and \metric{EUR 500K} in profits within 7 years. Built and led a \metric{9-person AI team}, recruiting 3 PhDs and 2 university professors across Italy and Argentina. Launched the GenAI Adoption business line, generating \metric{EUR 250K} in additional revenue in 15 months with a \metric{60\% profit margin}. Appointed CEO in 2023, driving a doubling of revenues within two years. In 2025, xtream was acquired by TeamSystem, a company with EUR 1.1B in revenues backed by CapitalG and the Abu Dhabi Investment Authority.}

  \cventry
    {Machine learning, time series forecasting, Python, scikit-learn, XGBoost, Azure, Databricks}
    {Financial index forecasting}
    {}
    {}
    {Led a team of 5 data scientists in the design and implementation of models to forecast financial indexes from macroeconomic variables. Implemented ingestion, preprocessing, training, and prediction on Azure Databricks and Data Factory. On a subset of the indexes, models outperformed the market and were used to support investment decisions.}

  \cventry
    {Machine learning, time series forecasting, Python, scikit-learn, project management}
    {Power load forecasting}
    {}
    {}
    {Led a team of 4 data scientists and data engineers from presales to deployment. Achieved an average Mean Absolute Percentage Error (MAPE) \metric{25\% lower} than the previous production system, delivered result-sharing presentations to top management, and was asked to enable use of the new models before deployment.}

  \cventry
    {GenAI, RAG, LangChain, OpenAI, Python, Qdrant}
    {AskHR}
    {}
    {}
    {Led a team of four engineers from presales through deployment to develop a Retrieval-Augmented Generation system that answers employee questions on HR policies. Built in close collaboration with the HR team of Europe's largest paytech company, the solution is now used by all Italian employees and reduced HR ticket volume by \metric{30\%} within the first two months.}

  \cventry
    {Reaidy}
    {Co-founder, CEO}
    {Milan, Italy}
    {2024--2025}
    {Co-founded and led the early development of Reaidy, an enterprise copywriting platform. Led pretotyping, prototyping, and delivery of initial product demos; secured the first clients; and generated \metric{EUR 230K} in revenue in the first year. Reaidy was acquired by TeamSystem in 2025.}

  \cventry
    {Techedge}
    {Data Scientist}
    {Milan, Italy and Madrid, Spain}
    {2015--2017}
    {Held this role as a part-time employee while attending MSc lessons. Achieved a 100\% success rate in the projects I participated in and helped grow one customer team from 2 to 8 people.}

  \cventry
    {Statwolf}
    {Data Scientist}
    {Dublin, Ireland and Pavia, Italy}
    {2015--2017}
    {Started as a summer intern in Dublin, then held a part-time remote collaboration. Delivered an analysis on the effect of weather conditions on the semiconductor manufacturing process. The results were praised by the customer and led to follow-up contracts for the company.}
\end{cventries}

\cvsection{Lecturing}
\begin{cventries}
  \cventry
    {}
    {Catholic University of Milan}
    {}
    {2025--current}
    {Professor for the class ``Practical AI'' in the Master of Science in Management \& Innovation. Received 8.4/9 in student satisfaction in the first year.}

  \cventry
    {}
    {Catholic University of Milan}
    {}
    {2024--current}
    {Member of the academic board for the master's degrees in Economics and Statistics.}

  \cventry
    {}
    {University of Pavia}
    {}
    {}
    {Proposed, designed, and lectured 3 editions of the short course ``Python for Data Science'' and 2 editions of ``Python for Data Analytics''. Sold out 5/5 editions and received 100\% positive or very positive feedback in surveys. Held the Machine Learning class in the Master's in Statistical Genomics.}

  \cventry
    {}
    {Almo Collegio Borromeo, Pavia}
    {}
    {}
    {Held ``Introduction to R Programming'' and ``Introduction to Machine Learning''.}
\end{cventries}

\cvsection{Education}
\begin{cventries}
  \cventry
    {University of Pavia, Italy and EPFL, Switzerland}
    {PhD in Applied Machine Learning}
    {}
    {2018--2021}
    {Completed while building xtream. Tutors: Prof. G. De Nicolao (University of Pavia) and Prof. G. Ferrari-Trecate (EPFL).
      \begin{cvitems}
        \item Developed natural gas demand forecasting models adopted by A2A, Italy's third-largest utility.
        \item Introduced a novel Bayesian approach to power grid identification, later built upon by research groups at EPFL Lausanne, ETH Zurich, and UC Berkeley.
        \item Published 9 papers in peer-reviewed international journals and conferences, including IEEE Transactions, receiving 156 citations.
      \end{cvitems}}

  \cventry
    {University of Pavia, Italy. Graduated cum laude.}
    {Master of Science in Embedded and Control Systems}
    {}
    {2015--2017}
    {}

  \cventry
    {University of Pavia, Italy. Graduated cum laude.}
    {Bachelor of Science in Computer Engineering}
    {}
    {2012--2015}
    {}
\end{cventries}

\cvsection{Volunteering and Public Speaking}
\begin{cventries}
  \cventry
    {}
    {Mentor at Lead the Future}
    {}
    {}
    {Selected to mentor bachelor's and master's students interested in careers in STEM.}

  \cventry
    {}
    {Speaker and Track Organiser}
    {}
    {}
    {Since 2023, delivered 50+ talks at major technical conferences across Europe, including PyData Paris, PyData Berlin, PyData Milan, Swiss Python Summit, Codemotion, WeAreDevelopers Berlin, AMLD Lausanne, ODSC London, PyCon Italy, PyCon Germany, and the Insurance Data Science Conference in London. Since 2022, organised and hosted conference tracks and workshops at AMLD Lausanne, Europe's leading applied AI conference.}
\end{cventries}

\cvsection{Public Resources}
\begin{cvparagraph}
\resource{Research}{https://scholar.google.com/citations?user=aK8MDJIAAAAJ}\\
\resource{Talks}{https://youtube.com/playlist?list=PLbrceUOJLNLSlZfIWXZCdXzTeVw3JSurG}\\
\resource{Articles}{https://medium.com/@donlelef}\\
\resource{Code}{https://github.com/donlelef}\\
\resource{Public speaking}{https://sessionize.com/emanuele-fabbiani/}
\end{cvparagraph}

\end{document}
